---
title: "p8105_hw1_jl6647"
author: "Jiatong Li"
date: "2023-09-14"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)

data(early_january_weather, package = "moderndive")
```

## HW1 Problem_1

### Description of datasets

The datasets include 15 variables: 

`origin`: Weather station. Named origin to facilitate merging with nycflights13::flights data.

`year`, `month`, `day`, `hour`: Time of recording.

`temp`,`dewp`: Temperature and dewpoint in F.

`humid`: Relative humidity.

`wind_dir`, `wind_speed`, `wind_gust`: Wind direction (in degrees), speed and gust speed (in mph).

`precip`: Precipitation, in inches.

`pressure`: Sea level pressure in millibars.

`visib`: Visibility in miles.

`time_hour`: Date and hour of the recording as a POSIXct date.

### Size of datasets

#### `nrow` and `ncol` is used when determining the size of datasets 

`Row`: `r nrow(early_january_weather)`

`Column`: `r ncol(early_january_weather)`

### Mean temperature

`Mean temperature`: `r mean(early_january_weather$temp)`

### A scatterplot of temp (y) vs time_hour (x)
  
```{r temp_time, echo=FALSE}
library(ggplot2)
  plot_1 <- ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + geom_point()
  plot_1
  ggsave("scatterplot.png", plot = plot_1)
```


## HW1 Problem_2

### Data Frame of numeric, logical, character and factor variables
```{r problem2_df,echo=FALSE}
library(tidyverse)
set.seed(1)
problem2_df <- tibble(
  norm_sample = rnorm(10),
  logi_vector = norm_sample > 0,
  char_vector = c("A", "B", "C", "D", "E", "F", "G", "H", "I", "J"),
  fact_vector = factor(c("Low", "Medium", "High", "Low", "Medium", "High", "Low", "Medium", "High", "Low"))
)
print(problem2_df)
```


### Apply `as.numeric` function to logical, character, and factor variables to interpret variables into numbers
```{r as.numeric}
as.numeric_norm <- as.numeric(pull(problem2_df,norm_sample))
as.numeric_logi <- as.numeric(pull(problem2_df,logi_vector))
as.numeric_char <- as.numeric(pull(problem2_df,char_vector))
as.numeric_fact <- as.numeric(pull(problem2_df,fact_vector))
```
### The mean of each variables
In the console, warning occurs as `argument is not numeric or logical: returning NA` when running character or factor vectors if `as.numeric` function does not apply
```{r mean_df,echo=FALSE}
mean(as.numeric_norm)    # Works, as it's a numeric variable
mean(as.numeric_logi)    # Works, as it's a numeric variable
mean(as.numeric_char)    # Won't work, character variable
mean(as.numeric_fact)    # Won't work, factor variable
```





